$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-04 paper/e6ssm-tuning-paper.tex
Added O(t^2) coefficient for m_u3^2
Added two-loop beta function for m_Q3^2

\beta_{m_{Q3}^2}^{(2)}&=,\label{eq:USSMmq222BetaTwoLoop}\\

@@

\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+4a_t^2-\frac{32}{3}g_3^2M_3^2-\frac{32}{15}g_1^1M_1^2-8Q_u^2g_1'^2M_1'^2\nonumber\\

@@

&{}-8Q_ug_1'^2\sum_{i=1}^3\left ( Q_1m_{H_d}^2+Q_2m_{H_u}^2+Q_Sm_S^2\right )\nonumber\\

@@

b_{m_{u3}^2}^{(2)}&=.\label{eq:USSMmu222Ot2Coeff}

>>>>

\beta_{m_{Q3}^2}^{(2)}&=-20y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2 \right )-20y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2 \right )\nonumber\\
&{}-2y_\tau^2y_b^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{L3}^2+m_{d3}^2+m_{e3}^2\right )-40y_t^2a_t^2-40y_b^2a_b^2\nonumber\\
&{}-2\left ( y_ba_\tau+y_\tau a_b\right )^2-2\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )\nonumber\\
&{}-2\lambda^2y_b^2\left ( m_{H_u}^2+2m_{H_d}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )-2\left ( \lambda a_t+y_t a_\lambda \right )^2-2\left ( \lambda a_b+y_b a_\lambda \right )^2\nonumber\\
&{}+\frac{2}{5}g_1^2y_t^2\left ( m_{H_u}^2+3m_{Q3}^2+8m_{u3}^2 +8M_1^2\right )+\frac{8}{5}g_1^2\left ( a_t^2-2y_ta_tM_1 \right )\nonumber\\
&{}+\frac{2}{5}g_1^2y_b^2\left ( 5m_{H_d}^2+m_{Q3}^2+4M_1^2\right )+\frac{4}{5}g_1^2\left ( a_b^2-2y_ba_bM_1 \right )+\frac{2}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
&{}+\frac{2}{5}g_1^2\sum_{i=1}^3\left [ \kappa_i^2\left ( m_{Di}^2-m_{\overline{D}i}^2\right )+\lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )\right ]\nonumber\\
&{}+4g_1'^2y_t^2\left ( Q_2^2-Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )\nonumber\\
&{}+4g_1'^2\left ( Q_2^2-Q_Q^2+Q_u^2\right )\left ( a_t^2 -2y_ta_tM_1'\right )-24Q_Qg_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q3}^2+Q_um_{u3}^2\right )\nonumber\\
&{}+4g_1'^2y_b^2\left ( Q_1^2-Q_Q^2+Q_d^2 \right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1'^2\right )\nonumber\\
&{}+4g_1'^2\left ( Q_1^2-Q_Q^2+Q_d^2\right )\left ( a_b^2-2y_ba_bM_1'\right )-24Q_Qg_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q3}^2+Q_dm_{d3}^2\right )\nonumber\\
&{}-8Q_Qg_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L3}^2+Q_em_{e3}^2\right )\nonumber\\
&{}-4Q_Qg_1'^2\sum_{i=1}^3\left [ 3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2\right )+2\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )\right ]\nonumber\\
&{}+\frac{16}{3}g_3^4\left [ 10M_3^2+\sum_{i=1}^3\left ( 2m_{Qi}^2+m_{ui}^2+m_{di}^2+m_{Di}^2+m_{\overline{D}i}^2\right )\right ]+32g_3^2g_2^2\left ( M_2^2+M_2M_3+M_3^2\right )\nonumber\\
&{}+\frac{16}{45}g_3^2g_1^2\left [ 2\left ( M_1^2+M_1M_3+M_3^2\right )+3\sum_{i=1}^3\left ( m_{Qi}^2+m_{di}^2-2m_{ui}^2-m_{Di}^2+m_{\overline{D}i}^2\right )\right ]\nonumber\\
&{}+\frac{32}{3}Q_Qg_3^2g_1'^2\bigg [ 4Q_Q\left ( M_1'^2+M_1'M_3+M_3^2 \right )+3\sum_{i=1}^3\big ( 2Q_Qm_{Qi}^2+Q_um_{ui}^2+Q_dm_{di}^2\nonumber\\
&{}+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2 \big )\bigg ]+g_2^4\left [ 87M_2^2+m_{\overline{H'}}^2+m_{H'}^2+3\sum_{i=1}^3\left ( 3m_{Qi}^2+m_{Li}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
&{}+\frac{1}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2 \right )+3m_{\overline{H'}}^2-3m_{H'}^2+3\sum_{i=1}^3\left ( m_{Qi}^2-m_{Li}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
&{}+12Q_Qg_2^2g_1'^2\bigg [ 2Q_Q\left ( M_1'^2+M_1'M_2+M_2^2\right )+Q_{\overline{H'}}m_{\overline{H'}}^2+Q_{H'}m_{H'}^2\nonumber\\
&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Qi}^2+Q_Lm_{Li}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{75}g_1^4\bigg [ 289M_1^2+12m_{\overline{H'}}^2-6m_{H'}^2\nonumber\\
&{}+\sum_{i=1}^3\left ( 6m_{di}^2-2m_{Di}^2+6m_{\overline{D}i}^2+42m_{ei}^2-6m_{H_i^d}^2+12m_{H_i^u}^2-6m_{Li}^2+2m_{Qi}^2-24m_{ui}^2\right )\bigg ]\nonumber\\
&{}+\frac{4}{15}g_1^2g_1'^2\bigg [ 2Q_Q\big ( 9Q_d+9Q_{\overline{D}}-9Q_D+9Q_e-9Q_1+9Q_2+3Q_{\overline{H'}}-3Q_{H'}-9Q_L\nonumber\\
&{}+10Q_Q-18Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}m_{H'}^2\nonumber\\
&{}+3\sum_{i=1}^3\big ( Q_d^2m_{di}^2+Q_{\overline{D}}^2m_{\overline{D}i}^2-Q_D^2m_{Di}^2+Q_e^2m_{ei}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2\nonumber\\
&{}-Q_L^2m_{Li}^2-Q_Q^2m_{Qi}^2-2Q_u^2m_{ui}^2\big )+15Q_QQ_{\overline{H'}}m_{\overline{H'}}^2+3Q_QQ_{H'}m_{H'}^2\nonumber\\
&{}+Q_Q\sum_{i=1}^3\big ( 12Q_dm_{di}^2+12Q_{\overline{D}}m_{\overline{D}i}^2+24Q_em_{ei}^2+3Q_1m_{H_i^d}^2+15Q_2m_{H_i^u}^2+3Q_Lm_{Li}^2\nonumber\\
&{}+15Q_Qm_{Qi}^2+12m_{ui}^2\big )\bigg ]+8Q_Qg_1'^4\bigg [ 3Q_QM_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2\nonumber\\
&{}+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2+20Q_Q^2+3Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2\nonumber\\
&{}+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )+2Q_QQ_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_QQ_{H'}^2m_{H'}^2\nonumber\\
&{}+Q_Q\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2\nonumber\\
&{}+2Q_L^2m_{Li}^2+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmq222BetaTwoLoop}\\

@@

\beta_{m_{u3}^2}^{(1)}&=4y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+4a_t^2-\frac{32}{3}g_3^2M_3^2-\frac{32}{15}g_1^2M_1^2-8Q_u^2g_1'^2M_1'^2\nonumber\\

@@

&{}-8Q_ug_1'^2\sum_{i=1}^3\lambda_i^2\left ( Q_1m_{H_d}^2+Q_2m_{H_u}^2+Q_Sm_S^2\right )\nonumber\\

@@

b_{m_{u3}^2}^{(2)}&=48y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2 \right )+4y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+m_{Q3}^2+m_{u3}^2+m_{d3}^2 \right )+96y_t^2a_t^2\nonumber\\
&{}+4\left ( y_ta_b+y_ba_t\right )^2+4\lambda^2y_t^2\left ( 2m_{H_u}^2+m_{H_d}^2+m_S^2+m_{Q3}^2+m_{u3}^2 \right )+4\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
&{}-\frac{64}{3}g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_3^2\right )-\frac{64}{3}g_3^2\left ( a_t^2-2y_ta_tM_3 \right )\nonumber\\
&{}-12g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_2^2\right )-12g_2^2\left ( a_t^2-2y_ta_tM_2\right )\nonumber\\
&{}-\frac{52}{15}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1^2\right )-\frac{52}{15}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
&{}-8g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )\nonumber\\
&{}-8g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( a_t^2-2y_ta_tM_1'\right )\nonumber\\
&{}+4g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 3Q_um_{H_u}^2+3Q_um_{Q3}^2+3Q_um_{u3}^2+\Sigma_1'\right )\nonumber\\
&{}+12Q_ug_1^2a_t^2\left ( Q_2+Q_Q+Q_u\right )+12Q_ug_1'^2y_b^2\left ( Q_1+Q_Q+Q_d \right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
&{}+12Q_ua_b^2\left ( Q_1+Q_Q+Q_d \right )\nonumber\\
&{}+4Q_ug_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+4Q_ua_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
&{}+Q_ug_1'^2\sum_{i=1}^3\bigg [ 6\kappa_i^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+6a_{\kappa_i}^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\nonumber\\
&{}+4\lambda_i^2\left ( Q_1+Q_2+Q_S\right )\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4a_{\lambda_i}^2\left ( Q_1+Q_2+Q_S\right )\bigg ]\nonumber\\
&{}-96Q_ug_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )\nonumber\\
&{}-12Q_ug_2^2g_1'^2M_2^2\left ( 9Q_Q+3Q_L+3Q_1+3Q_2+Q_{H'}+Q_{\overline{H'}}\right )-\frac{384}{25}g_1^4\left ( \Sigma_1+4M_1^2\right )\nonumber\\
&{}+\frac{2}{5}g_1^2g_1'^2\big [ 8M_1'^2 ( 3Q_d^2+3Q_{\overline{D}}^2-3Q_D^2+3Q_e^2-3Q_1^2+3Q_2^2+Q_{\overline{H'}}^2-Q_{H'}^2-3Q_L^2\nonumber\\
&{}+3Q_Q^2-6Q_u^2 )+6Q_uM_1^2 ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}\nonumber\\
&{}+3Q_L+Q_Q+8Q_u )+\left ( 3Q_u\Sigma_1-2\Sigma_1^\prime\right ) ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+3Q_2\nonumber\\
&{}+Q_{\overline{H'}}-Q_{H'}-3Q_L+3Q_Q-6Q_u )\big ]-4Q_ug_1'^4\big [ 2M_1'^2 ( 9Q_d^3+9Q_D^3+9Q_{\overline{D}}^3+3Q_e^2\nonumber\\
&{}+6Q_1^2+6Q_2^2+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3 )\nonumber\\
&{}+\left(6Q_uM_1'^2-\Sigma_1^\prime\right )( 9Q_d^2+9Q_D^2+9Q_{\overline{D}}^2+3Q_e^2+6Q_1^2+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2\nonumber\\
&{}+6Q_L^2+18Q_Q^2+3Q_S^2+9Q_u^2 )\big ].\label{eq:USSMmu222Ot2Coeff}
